Application of Machine Learning to Predict the Optoelectronic Properties of Benzobisazoles

### 2014-07-01 paper/paper.tex
Add updates to the paper

One problem with the first decay type feature vector is it makes the assumption that all the distances between are the same length. Since the effects of atoms are highly dependent on distance this sort of assumption is problematic for heterogeneous side groups. \eqref{decay2} Something something. This normalizes all the lengths such that longer structures will increase the distance more than shorter structures.

@@

\hl{????}
\subsection{Mean Value}
\subsection{Linear Regression}
\subsection{Linear Ridge Regression}
\subsection{Tree Regression}
\subsection{k-Nearest Neighbors}
\subsection{Support Vector Machines}
\subsubsection{Gaussian Kernel}
\subsubsection{Laplacian Kernel}
\hl{????}

 \begin{figure}[H]
   \begin{center}
     \includegraphics[width=5in]{figures/surf.png}
   \end{center}
   \caption{Example scan of test errors (eV) as a function of SVM parameters C and $\gamma$. The minimum located in the center corresponding to the ideal pair of parameter values to use for the machine learning model.}
   \label{fig:scan}
 \end{figure}

@@

Roughly 1100 benzobisazole structures were picked to to cover as many combinations of cores, sides, and options as possible. In terms of Aryl triplets, all of the structures comprised of at most 4 triplets per side. (This allowed for a constant vector size for the naive feature vector.) (Many of these structures were from prior studies of different features of benzobisazoles) Once they were built the structures were optimized using Density Functional Theory (DFT) with B3LYP/6-31g*. After the optimization, the molecules were then ran with Time Dependent Density Functional Theory (TDDFT) with B3LYP/6-31g*. Beyond the 1100 benzobisazole structures, about 1000 other structures were collected for comparison. The DFT calculations were done using the computing cluster Marcy from Bucknell and Gaussian 09. The machine learning algorithms used were the ones implemented in the \hl{Scikit-Learn Python Library}.

>>>>

One problem with the first decay type feature vector is it makes the assumption that all the distances between are the same length. Since the effects of atoms are highly dependent on distance this sort of assumption is problematic for heterogeneous side groups. \eqref{decay2} \hl{Something something}. This normalizes all the lengths such that longer structures will increase the distance more than shorter structures.

@@

\hl{???? information about the different methods used?}
% \subsection{Mean Value}
% \subsection{Linear Regression}
% \subsection{Linear Ridge Regression}
% \subsection{Tree Regression}
% \subsection{k-Nearest Neighbors}
% \subsection{Support Vector Machines}
% \subsubsection{Gaussian Kernel}
% $$k(x, x') = exp\left( - \frac{1}{2 \sigma^2} || x - x' ||^2 \right)$$
% \subsubsection{Laplacian Kernel}
% $$k(x, x') = exp\left( - \frac{1}{\sigma} | x - x' | \right)$$

 \begin{figure}[H]
   \begin{center}
     \includegraphics[width=5in]{figures/surf.png}
   \end{center}
   \caption{Example scan of test errors (eV) as a function of SVM parameters C and $\gamma$. The minimum located in the center corresponding to the ideal pair of parameter values to use for the machine learning model. Similar scan procedures were done for the parameters of the other models to find the lowest testing error.}
   \label{fig:scan}
 \end{figure}

@@

Roughly 1100 benzobisazole structures were picked to to cover as many combinations of cores, sides, and options as possible. In terms of Aryl triplets, all of the structures comprised of at most 4 triplets per side. (This allowed for a constant vector size for the naive feature vector.) (Many of these structures were from prior studies of different features of benzobisazoles) Once they were built the structures were optimized using Density Functional Theory (DFT) with B3LYP/6-31g*. After the optimization, the molecules were then ran with Time Dependent Density Functional Theory (TDDFT) with B3LYP/6-31g*. \hl{Beyond the 1100 benzobisazole structures, about 1000 other structures were collected for comparison.} The DFT calculations were done using the computing cluster Marcy from Bucknell and Gaussian 09. The machine learning algorithms used were the ones implemented in the \hl{Scikit-Learn Python Library}.
